---
title: "Untitled"
author: "Jushua Espadon"
date: "2023-10-10"
output: pdf_document
---

#NUMBER 1
#A.
``` {r num1a}
household <- data.frame (
  Respondents = 1:20, 
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2), 
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1), 
  Person_at_Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_school = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  Types_of_houses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)
household
```
#B.
``` {r num1b}
str(household)
summary(household)
```

#C.
``` {r num1c}
mean_siblings <- mean(household$Siblings_at_school)
mean_siblings == 5
```

#D.
``` {r num1d}
subset1 <- household[1:2, ]
subset1
```

#E.
``` {r num1e}
subset2 <- household[c(3, 5), c(2, 4)]
subset2
```
#F.
``` {r num1f}
types_houses <- household$Types_of_houses
types_houses
```
#G.
``` {r num1g}
male_farmer <- subset(household, Sex == 1 & Fathers_Occupation == 1)
male_farmer
```

#H.
``` {r num1h}
female_greater_than_5_siblings <- subset(household, Sex == 2 & Siblings_at_school >= 5)
female_greater_than_5_siblings
```

#NUMBER 2
``` {r num2} 
df <- data.frame(
  Ints = integer(),
  Doubles = double(),
  Characters = character(),
  Logicals = logical(),
  Factors = factor(),
  stringsAsFactors = FALSE
)
cat("Structure of the empty dataframe:\n")
str(df)
```
#Output
The output shows that the data frame has 0 observations (rows) and 5 variables (columns) with their respective data types. The "Factors" column is empty since there are no levels defined yet.

#NUMBER 3
``` {r num3}
household_data <- data.frame (
  Respondents = 1:10, 
  Sex = c("Male", "Female", "Female", "Male", "Male", "Female", "Female", "Male", "Female", "Male"), 
  Fathers_Occupation = c(1,2,3,3,1,2,2,3,1,3), 
  Person_at_Home = c(5,7,3,8,6,4,4,2,11,6),
  Siblings_at_school = c(2,3,0,5,2,3,1,2,6,2),
  Types_of_houses = c("Wood", "Congrete", "Congrete", "Wood", "Semi-Congrete", "Semi-Congrete", "Wood", "Semi-Congrete", "Semi-Congrete", "Congrete")
)
household_data
write.csv(household_data, file = "HouseholdData.csv", row.names = FALSE)
```
#A.
``` {r num3a}
household_data <- read.csv("HouseholdData.csv")
```
#B.
``` {r num3b}
household_data$Sex <- factor(household_data$Sex)
household_data$Sex <- as.integer(factor(household_data$Sex, 
                                 levels = c("Male", "Female"),
                                    labels = c(1, 2)))
household_data
```
#C.
``` {r num3c}
household_data$Types_of_houses <- factor(household_data$Types_of_houses)
household_data$Types_of_houses <- as.integer(factor(household_data$Types_of_houses,
                                              levels = c("Wood", "Congrete", "Semi-Congrete"),
                                                    labels = c(1, 2, 3)))
print(household_data)
```

#D.
``` {r num3d}
household_data$Fathers_Occupation <- factor(household_data$Fathers_Occupation)
household_data$Fathers_Occupation <- as.character(factor(household_data$Fathers_Occupation,
                                            
                                            levels = c(1, 2, 3),
                                            labels = c("Farmer", "Driver", "Others")))

# Print the updated data frame
print(household_data)


```

#E.
``` {r num3e}
female_driver <- subset(household_data, Sex == 2 & Fathers_Occupation == "Driver")
female_driver
```

#F.
``` {r num3f}
greater_than_5_siblings <- subset(household_data, Siblings_at_school >= 5)
greater_than_5_siblings
```
#4. INTERPRET THE GRAPH
Specifically for the dates July 14, 15, 17, 18, and 21 in the year 2020, the graph you've presented seems to be a sentiment analysis over time on Twitter data. Twitter posts are divided into three sentiment categories by the sentiment analysis: negative, neutral, and positive. The data are interpreted as follows:

July 14, 2020:
Negative tweet count: Nearly 2,500 tweets fell into this category.
The number of neutral tweets was approximately 1,500.
Positive tweet count: 1,750 tweets were considered to be positive.

July 15, 2020:
Negative tweet count: More than 4,000 tweets were marked as such.
The number of neutral tweets was approximately 2,750.
3,200 or so tweets were labeled as positive, according to the positive count.

July 17, 2020:
Number of tweets classified as negative: There were roughly 3,250 tweets in this category.
Neutral number:
You sent
Neutral tweets were assigned a count of about 1,800.
Positive tweet count: Nearly 2,500 tweets fell into the positive category.

July 18, 2020:
Negative tweet count: As of this writing, 3,250 tweets had been classified as negative.
The number of neutral tweets: Around 2,000 tweets were designated as neutral.
Positive tweet count: Around 2,500 tweets were identified as being positive.

July 20, 2020:
Negative tweet count: There were around 2,500 tweets that fell under this category.
The number of neutral tweets was approximately 1,500.
Positive tweet count: Nearly 1,750 tweets fell into the positive category.

July 21, 2020:
Negative tweet count: Approximately 4,000 tweets were designated as such.
Number of neutral tweets: 2,600 tweets in total were designated as neutral.
3,300 or so tweets were deemed to be positive, according to the positive count.